%1.Introduction to Beamer 
%2.Blocks and Columns 
%3.Overlays 
%4.Customize Themes 
%5.Aspect Ratio 
%6.Recapitulate 

\documentclass[dvipsnames, aspectratio=169]{beamer} 

% Packages 
\usetheme{Madrid} %theme 
\usecolortheme{default} %color theme  
\usepackage{color} %use color 
\setbeamercolor{structure}{fg=Green} %customize theme  
\usepackage{verbatim} %write latex code 

%Title Page 
\title{Introduction to {\LaTeX} for Researchers} 
\author[Jubayer Hossain]{\Large Jubayer Hossain}
\institute[HDRO]{\Large Health Data Research Organization} 
\date{\today}



\begin{document}
	\begin{frame}
		\maketitle 
	\end{frame}

	\section{What is {\LaTeX}?} 
	\begin{frame}[t]{What is {\LaTeX}?}\vspace{10pt}
		\begin{itemize}
			\item Document preparation system 
			\item {\LaTeX} was written by \textbf{Leslie Lamport} 
			\item Free software 
			\item License: LaTeX Project Public License 
			\item Website: \url{https://www.latex-project.org/}
		\end{itemize}
	\end{frame}

	\section{What's Different?} 
	\begin{frame}[t]{What's Different?}\vspace{10pt}
		\begin{itemize}
			\item It is not WYSIWYG.
			\item Concentrate on content writing and not formatting.
			\item Write simple commands for formatting.
			\item Write content and complex mathematical formulae with ease. 
		\end{itemize}
	\end{frame}

	\section{What can be done?} 
	\begin{frame}[t]{What can be done?}\vspace{10pt} 
		\begin{itemize}
			\item Write articles, books, scientific journals and papers.
			\item Design posters, banners, presentation, resume etc.
			\item Mostly used by writers and engineers.
		\end{itemize}
	\end{frame}

	\section{Why{\LaTeX}?} 
	\begin{frame}[t]{Why {\LaTeX}?} \vspace{10pt} 
	\begin{itemize}
		\item Quality and Aesthetics.
		\item Price
		\item Editing, Versioning and Outputs
		\item Focus on Content
		\item Time Investment
		\item Longevity
	\end{itemize}
	\end{frame}


	\section{Process of Writing} 
	\begin{frame}[t]{Process of Writing}\vspace{10pt}
	\begin{itemize}
		\item Write content using any text editor.
		\begin{itemize}
			\item notepad
			\item gedit
			\item {\LaTeX} IDEs(TexStudio, Texmaker)
		\end{itemize}
		\item Save it as .tex file 
		\item Output: .tex File(Input) $\longrightarrow$  
		pdflatex .tex(Build) $\longrightarrow$  .pdf File(Output)
	\end{itemize}
	\end{frame}

	\section{Some Sample {\LaTeX} Documents} 
	\begin{frame}[t]{Some Sample {\LaTeX} Documents} \vspace{10pt}
		\begin{itemize}
			\item Show some sample {\LaTeX} documents
			\item Comparison with other word processor(Microsoft Word, Google 
			Doc etc.)
		\end{itemize}
	\end{frame}

	\section{Install \LaTeX} 
	\begin{frame}[t]{Install \LaTeX} \vspace{10pt}
		\begin{itemize}
			\item Windows\\
			\url{https://miktex.org/}
			\item Linux(Ubuntu) \\ 
			sudo apt install texlive-latex-extra
		\end{itemize}
	\end{frame}


	\section{{\LaTeX} Offline IDEs/Editors}
	\begin{frame}[t]{{\LaTeX} Offline IDEs/Editors}\vspace{10pt}
		\begin{itemize}
			\item TexStudio \\
			\url{https://www.texstudio.org/}
			\item Texmaker \\
			\url{https://www.xm1math.net/texmaker/}
			\item Kile \\
			\url{https://kile.sourceforge.io/}
			\item TeXworks \\
			\url{http://www.tug.org/texworks/}
		\end{itemize}
	\end{frame}

	\section{{\LaTeX} Online IDEs}
	\begin{frame}[t]{{\LaTeX} Online IDEs/Editors}\vspace{10pt}
	\begin{itemize}
		\item Sharelatex/Overleaf \\
		 \url{https://www.overleaf.com/}
		\item Latexbae \\ 
		\url{https://latexbase.com/d/1648f17f-f52f-4653-8bca-7c9066c9a8de}
		\item CoCalc \\
		\url{https://cocalc.com/doc/latex-editor.html}
	\end{itemize}
	\end{frame}

	\section{How to choose {\LaTeX} IDEs/Editors}
	\begin{frame}[t]{How to choose {\LaTeX} IDEs/Editors}\vspace{10pt}
	\begin{itemize}
		\item Auto complete of {\LaTeX} commands. 
		\item Parenthesis matching. 
		\item Collapsible sections
		\item Inverse search
		\item Collaboration 
		\item Public project 
		\item Private project 
		\item Track changes 
		\item History 
		\item Comments \\ 
		See More: \url{https://en.wikipedia.org/wiki/Comparison_of_TeX_editors}
	\end{itemize}
	\end{frame}
	
	\section{Resources} 
	\begin{frame}[t]{Resources}\vspace{10pt}
	\begin{itemize}
		\item \url{https://www.latex-project.org/help/documentation/}
		\item \url{https://www.overleaf.com/learn}
		\item \url{https://www.latex-tutorial.com/}
		\item \url{https://www.latextemplates.com/} 
		\item \url{https://en.wikibooks.org/wiki/LaTeX/Mathematics}
	\end{itemize}
	\end{frame}

	\section{You'll Learn \dots}
	\begin{frame}[t]{You'll Learn \dots} \vspace{10pt}
		\begin{itemize}
			\item Introduction
			\item Sections and Levels 
			\item Content Formatting
			\item Ordered and Unordered List 
			\item Nested List 
			\item Inserting Images 
			\item Inserting Tables 
			\item Page Styles 
			\item Reference Management using BibTeX and Mendeley 
			\item Presentation using Beamer 
		\end{itemize}
	\end{frame}

	\section{Projects}
	\begin{frame}[t]{Projects}\vspace{10pt}
	\begin{enumerate}
		\item Report / Assignment Writing 
		\item Thesis Writing
		\item Research Paper  Writing
		\item Conference Poster Design 
	
	\end{enumerate}
	\end{frame}
	
	
	\begin{frame}
		\centering \LARGE Let's Start Coding \dots!
	\end{frame}
	
\end{document}